Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-28 sections/results.tex
add cross validation table

\begin{table*}[!t]
\caption{An accuracy of similarity and dissimilarity thresholds for useful and useless comment classifications}
\small
\centering
\def\arraystretch{1.2}
\begin{tabular}{ccccccc}
\hline
Prediction Models & $s_t$ & $d_t$ & F-measure & Precision & Recall \\ \hline \hline
$\Theta(c,S_T=s_t,D_T=d_t)$   & 0.015529 & 2.494944 & 0.741 & 0.701 & 0.787 \\ \hline
$\Omega(c,S'_T=s_t,D'_T=d_t)$ & 1 & 0.087522 & 2.265679 & 0.725 & 0.648 & 0.824 \\ \hline
\end{tabular}
\label{tb:thresholds}
\end{table*}

\textbf{Model Effectiveness.}
Figure \ref{fig:scatter} shows relationship between comments class and our similarity thresholds.
The green area represents the \emph{useful} classification model $\Theta(c,S_T=0.015529,D_T=2.494944)$, and the red area represents the \emph{useless} model $\Omega(c,S_T=0.087522,D_T=2.265679)$.
This figure also shows an example comment that fall in the different area\pick{Didn't put yet}.

@@

\textbf{Model Robustness.} After we performed cross validation, we obtained the following result:
for useful and useless classifications,
we obtained an average F$_1$ score of 0.693 and 0.681,
with standard deviation of 0.090 and 0.118, respectively.
This indicates that we can use our approach to classify with confident of 69.8\%.
\pick{Precision? Recall?} \thai{This is some confidence interval...}

>>>>

\textbf{Model Effectiveness.}
Figure \ref{fig:scatter} shows relationship between comments class and our similarity thresholds.
The green area represents the \emph{useful} classification model $\Theta(c,S_T=0.015529,D_T=2.494944)$, and the red area represents the \emph{useless} model $\Omega(c,S'_T=0.087522,D'_T=2.265679)$.
% This figure also shows an example comment that fall in the different area\pick{Didn't put yet}.
% Thai sez: Comment examples are in the discussion.

@@

\textbf{Model Robustness.} After we performed bootstrapping cross validation, we obtained the result as shown in Table \ref{tb:xvalidate}.
\thai{How to explain this table? Maybe with some kind of confidence interval? How to calculate it? (I tried the Confidence Interval calculator and the result is plain wrong.) Wow.}

\newcommand{\SampleMean}{$\bar{x}$}
\newcommand{\SampleSD}{$s$}

\begin{table*}[!t]
\caption{An accuracy of similarity and dissimilarity thresholds for useful and useless comment classifications}
\small
\centering
\def\arraystretch{1.2}
\begin{tabular}{ccccccc}
\hline
Prediction Models & $s_t$ & $d_t$ & F-measure & Precision & Recall \\ \hline \hline
$\Theta(c,S_T=s_t,D_T=d_t)$   & 0.015529 & 2.494944 & 0.741 & 0.701 & 0.787 \\ \hline
$\Omega(c,S'_T=s_t,D'_T=d_t)$ & 0.087522 & 2.265679 & 0.725 & 0.648 & 0.824 \\ \hline
\end{tabular}
\label{tb:thresholds}
\end{table*}

\begin{table*}[!t]
\caption{Bootstrapping cross validation result of our model. For each metric, we included the average and standard deviation.}
\small
\centering
\def\arraystretch{1.2}
\begin{tabular}{ccccccc}
\hline
\multirow{2}{*}{Prediction Models} & \multicolumn{2}{c}{F-measure} & \multicolumn{2}{c}{Precision} & \multicolumn{2}{c}{Recall} \\
& \SampleMean & \SampleSD & \SampleMean & \SampleSD & \SampleMean & \SampleSD \\ \hline \hline
$\Theta(c,S_T=s_t,D_T=d_t)$   & 0.693 & 0.089 &  0.654 & 0.116 &  0.759 & 0.123 \\
$\Omega(c,S'_T=s_t,D'_T=d_t)$ & 0.681 & 0.118 &  0.636 & 0.144 &  0.755 & 0.148 \\
\hline
\end{tabular}
\label{tb:xvalidate}
\end{table*}
